### 2018-11-25 Sections/essay_security_implications_of_the_global_quantum_internet.tex
John kelly

Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}\footnote{\textit{``I don't even know why any of us are here. This is the worst job I've ever had."}}.

>>>>

Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}\footnote{\famousquote{I don't even know why any of us are here. This is the worst job I've ever had.}{John Kelly}}.
